Carbonate chemistry at Ny-Ålesund

### 2021-12-27 awipev-CO2.Rmd
addessing outliers in sal_insitu_ctd cleaning up

library("RColorBrewer")
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)
if (!require("pangaear")) install.packages("pangaear")
library("pangaear")
if (!require("todor")) install.packages("todor")
library("todor")

@@

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", ylab = "y", proplot = TRUE, ...) 
  { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
#reg <- fit$regression.results[ty,] #one selects OLS only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
error <- xdata - predicted
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = title,
       subtitle = paste("\ntype: ", type,
                     "; R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "\nP =", signif(fit$P.param, 3),
                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
       x = xlab,
       y = ylab) +
#    lims(x = c(min(fit_data$xdata), max(fit_data$xdata)), y = c(min(fit_data$ydata), max(fit_data$ydata))) +
    theme_bw() +
    theme(plot.title = element_text(size = 10, face = "bold"),
          plot.subtitle = element_text(size = 8))
    if (proplot == TRUE) { # property-property plot
      plt <- plt +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        theme(aspect.ratio = 1)
    }
  return(list(plot = plt, fit = fit))
  } else {
  return(fit)
    }
}

@@

@@

salmixinterp <- approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, 
                       method="linear", rule = 2, , ties = "ordered")
names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
salmixinterp <- as.data.frame(salmixinterp)
d_all$sal_fb_mix_interp <- salmixinterp$sal_fb_mix_interp

@@

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
p_avail <- pivot_longer(z, -Flag) %>% 
  drop_na() %>% 
  ggplot(aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
kable(z, digits = 1)
# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(montht, pco2_fb, phINT)
count_pco2_fb_no_NA <- sum(!is.na(d2$pco2_fb)) # total non-NA pCO2 values
count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
# calculate the distribution of non-NA pCO2 and pH values per month
d2_summary <- d2 %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
                   )
# plot the distribution of non-NA pCO2 and pH values per month
p_avail_month <- d2_summary %>% 
  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc)) %>% 
  ggplot() +
  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
  labs(x="Month", y="Percent of total number of data", title = "") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
#ggsave(filename = "figures/monthly_availability.png", plot = p_avail_month, width = 15, height = 8, units = "cm")

# Combine plots
p <- (p_avail / p_avail_month)
p <- p + plot_annotation(tag_levels = 'A')
p
ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")

@@

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_fb_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_fb_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") & sal_fb_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_fb_mix < 34 ~ NA_real_,
      TRUE ~ sal_fb_mix
    )
  )
```

@@

```{r, eval=FALSE, echo=FALSE}
Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.

@@

### **Sal FB / Sal CTD 10 m**

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
reg <- ggreg(
  xdata = d_all$sal_insitu_ctd_10m,
  ydata = d_all$sal_fb,
  type = "MA",
  plot = TRUE,
  title = "Comparison salinity",
  #subtitle = "",
  xlab = "Salinity CTD 10 m",
  ylab = "Salinity FB",
  proplot = TRUE,
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

There are `r sum(!is.na(tmp$range))` days with temperature values at
both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
and 9 m ranges between `r min(tmp$range, na.rm=TRUE)`°C and
`r max(tmp$range, na.rm=TRUE)`°C (mean:
`r mean(tmp$range, na.rm=TRUE)`°C; `r median(tmp$range, na.rm=TRUE)`°C).
The difference with depth is therefore significant.

### **T Ferrybox / T insitu 11 m**

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
        datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )
lm <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_10m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_10m, y= temp_insitu_11m, label = monthd))+
  geom_text( aes(color=factor(monthd))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
                     "; Intercept =", signif(lm$intercept_MA, 3),
                     "; Slope =", signif(lm$slope_MA, 3),
                     "; P =", signif(lm$P, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)

@@

# above is old code. now we use sal_insitu_ctd_mix
salinterp <-
  approx(
    d_all$datetime,
    d_all$sal_insitu_ctd_mix,
    xout = d_all$datetime,
    method = "linear",
    rule = 2
  )
names(salinterp) <- c("datetime", "sal_insitu_ctd_mix_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_mix_interp

@@

```{r durafet clean up, echo=FALSE, message= FALSE, warning=FALSE}
d_all <- d_all %>% 
  dplyr::mutate(pH_dur = ph_dur_corr) %>% # the right durafet pH at in situ temp from now on
  dplyr::select(-ph_dur, -ph_dur_corr)
# normalized durafet pH 4°C
tmp <- d_all %>%
  dplyr::select(datetime, at, sal_fb, temp_fb, pH_dur) %>%
  tidyr::drop_na()
tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4 ), by="datetime")
```
## Range per months

@@

```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize ph_calc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb, temp_fb, ph_calc_fb, at)%>%
  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb))
pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")

@@

```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis using mean discrete values
# first, order columns
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all))) %>% 
  dplyr::select(datetime, date, year, monthd, montht, everything())
# calculate means of discrete values
mean_ct <- mean(discrete$ct, na.rm = TRUE)
mean_at <- mean(discrete$at, na.rm = TRUE)
mean_pco2 <- mean(discrete$pco2_calc_fb, na.rm = TRUE)
mean_sal <- mean(discrete$sal_fb, na.rm = TRUE)
mean_temp <- mean(discrete$temp_fb, na.rm = TRUE)
mean_discrete <- tibble(mean_ct = mean_ct, mean_at = mean_at, mean_pco2 = mean_pco2, mean_sal = mean_sal, mean_temp = mean_temp)

@@

  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
  dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 

@@

                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",

@@

                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",

@@

                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",

@@

                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",

@@

  #               ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb, temp_fb) %>%

@@

carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 

@@

  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 

>>>>

library("RColorBrewer")
if (!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)
if (!require("seacarb")) install.packages("seacarb")
library("seacarb")
if (!require("gridExtra")) install.packages("gridExtra")
library("gridExtra")
if (!require("lubridate")) install.packages("lubridate")
library("lubridate")
if (!require("grid")) install.packages("grid")
library(grid)
if (!require("viridis")) install.packages("viridis")
library("viridis")
if (!require("dygraphs")) install.packages("dygraphs")
library("dygraphs")
if (!require("knitr")) install.packages("knitr")
require("knitr")
if (!require("lmodel2")) install.packages("lmodel2")
library("lmodel2")
if (!require("captioner")) install.packages("captioner")
library("captioner")
if (!require("xts")) install.packages("xts")
library("xts")
if (!require("scales")) install.packages("scales")
library("scales")
if (!require("skimr")) install.packages("skimr")
library("skimr")
if (!require("FNN")) install.packages("FNN")
library("FNN")
if (!require("patchwork")) install.packages("patchwork")
library("patchwork")
if (!require("pander")) install.packages("pander")
library("pander")
if (!require("tsibble")) install.packages("tsibble")
library("tsibble")
if (!require("slider")) install.packages("slider")
library("slider")
if (!require("kableExtra")) install.packages("kableExtra")
library("kableExtra")
if (!require("readxl")) install.packages("readxl")
library("readxl")
if (!require("oce")) install.packages("oce")
library(oce)
if (!require("pangaear")) install.packages("pangaear")
library("pangaear")
if (!require("todor")) install.packages("todor")
library("todor")
# todor::todor_file("awipev-CO2.Rmd")

@@

#################### Regression function
# function regression plot with equation (MA or OLS) in title
ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", 
                   ylab = "y", proplot = TRUE, ...) 
  { # x and y are the names of the variables
  fit_data <- tibble(xdata, ydata)
  colnames(fit_data) = c("xdata", "ydata")
  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
if (type == "OLS") ty = 1 #one selects OLS only
if (type == "MA") ty = 2 #one selects MA only
intercept <- fit$regression.results$Intercept[ty]
slope <- fit$regression.results$Slope[ty]
predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
error <- xdata - predicted
if (plot == TRUE) {
  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
  geom_abline(aes(intercept = intercept, slope = slope),
              colour = "blue")  + 
  labs(title = title,
       subtitle = paste("\ntype: ", type,
                     "; R2 = ", round(fit$rsquare, digits = 2),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "\nP =", signif(fit$P.param, 3),
                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
       x = xlab,
       y = ylab) +
    theme_bw() +
    theme(plot.title = element_text(size = 10, face = "bold"),
          plot.subtitle = element_text(size = 8))
    if (proplot == TRUE) { # property-property plot
      plt <- plt +
        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
        theme(aspect.ratio = 1)
    }
  return(list(plot = plt, fit = fit))
  } else {
  return(fit)
    }
}

@@

# To address the issues of sal_insitu_ctd (many outliers, see figure in tab salinities)
# the impossibly low values are identified using the threshold of the 
# minimum salinity measured in the FerryBox - 0 unit
d_hour <- d_hour %>% 
  dplyr::mutate(sal_insitu_ctd = ifelse(sal_insitu_ctd < min(sal_fb, na.rm = TRUE) - 0 |
                                        sal_insitu_ctd > 36,  # 2 outliers
                                        sal_fb, sal_insitu_ctd))

@@

salmixinterp <- approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, 
                       method="linear", rule = 2, ties = "ordered")
names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
salmixinterp <- as.data.frame(salmixinterp)
d_all$sal_fb_mix_interp <- salmixinterp$sal_fb_mix_interp

@@

s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
# durafet and seafet started later
x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
  as.data.frame() %>%
         rownames_to_column(var = "flag") %>% 
         as_tibble()
labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
p_avail <- pivot_longer(z, -Flag) %>% 
  drop_na() %>% 
  ggplot(aes(x = name, y = value, fill = Flag)) +
  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
  scale_fill_discrete(labels = labels) + 
  coord_flip() +
  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
kable(z, digits = 1)
# Monthly distribution of hourly data
d2 <- d_all %>% 
  dplyr::select(montht, pco2_fb, phINT)
count_pco2_fb_no_NA <- sum(!is.na(d2$pco2_fb)) # total non-NA pCO2 values
count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
# calculate the distribution of non-NA pCO2 and pH values per month
d2_summary <- d2 %>% 
  dplyr::group_by(montht) %>% 
  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
                   )
# plot the distribution of non-NA pCO2 and pH values per month
p_avail_month <- d2_summary %>% 
  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc)) %>% 
  ggplot() +
  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
  labs(x="Month", y="Percent of total number of data", title = "") +
  Mytheme(size_labs = 8) +
  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
# Combine plots
p <- (p_avail / p_avail_month)
p <- p + plot_annotation(tag_levels = 'A')
p
ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")

@@

```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# SAL FerryBox and sal_fb_mix
sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
  dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyLegend(show = "follow")   %>%
  dyAxis("y", valueRange = c(30, 37)) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
# now remove outliers
d_all <- d_all %>%
  dplyr::mutate(
    sal_fb_mix = case_when(
      date > as.Date("2016-02-01") &
        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
      date > as.Date("2015-10-01") &
        date <  as.Date("2015-10-05") &
        sal_fb_mix < 31.5 ~ NA_real_,
      date == as.Date("2017-03-22") &
        sal_fb_mix < 34 ~ NA_real_,
      TRUE ~ sal_fb_mix
    )
  )
```

@@

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.

@@

### **Comparison salinity FerryBox vs Salinity CTD REMOS 10 m** 
```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
# REVIEW OK?
reg <- ggreg(
  xdata = d_all$sal_insitu_ctd_10m,
  ydata = d_all$sal_fb_mix,
  type = "MA",
  plot = TRUE,
  title = "Comparison salinity",
  #subtitle = "",
  xlab = "Salinity CTD REMOS 10 m",
  ylab = "Salinity FerryBox",
  proplot = TRUE,
  ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

```{r, eval=FALSE, echo=FALSE}
# skipped because it is done in the "stratification tab"
There are `r sum(!is.na(tmp$range))` days with temperature values at
both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
and 9 m ranges between `r min(tmp$range, na.rm=TRUE)`°C and
`r max(tmp$range, na.rm=TRUE)`°C (mean:
`r mean(tmp$range, na.rm=TRUE)`°C; `r median(tmp$range, na.rm=TRUE)`°C).
The difference with depth is therefore significant.
```

### **Temperature Ferrybox vs Temperature in situ 11 m** 
```{r, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
      datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )

reg <- ggreg(
  xdata = d_all$temp_insitu_11m,
  ydata = d_all$temp_fb,
  type = "MA",
  plot = TRUE,
  title = "Comparison temperature",
  #subtitle = "",
  xlab = "Temperature in situ 11 m",
  ylab = "Temperature FerryBox",
  proplot = TRUE,
  ylim(c(-2, 8.5)) + xlim(c(-2, 8.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
reg <- ggreg(
  xdata = d_all$temp_insitu_ctd_10m,
  ydata = d_all$temp_insitu_11m,
  type = "MA",
  plot = TRUE,
  title = "Comparison temperature",
  #subtitle = "",
  xlab = "Temperature CTD REMOS 10 m",
  ylab = "Temperature in situ 11 m",
  proplot = TRUE,
  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
  coord_fixed(ratio = 1)
)
print(reg$plot)

@@

# above is old code. Now we use sal_insitu_ctd_mix
salinterp <-
  approx(
    d_all$datetime,
    d_all$sal_insitu_ctd_mix,
    xout = d_all$datetime,
    method = "linear",
    rule = 2
  )
names(salinterp) <- c("datetime", "sal_insitu_ctd_mix_interp")
salinterp <- as.data.frame(salinterp)
d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_mix_interp

@@

```{r durafet clean up, echo=FALSE, message= FALSE, warning=FALSE}
d_all <- d_all %>% 
  dplyr::mutate(pH_dur = ph_dur_corr) %>% # the right durafet pH at in situ temp from now on
  dplyr::select(-ph_dur, -ph_dur_corr)
# normalized durafet pH 4°C
tmp <- d_all %>%
  dplyr::select(datetime, at, sal_fb_mix, temp_fb, pH_dur) %>%
  tidyr::drop_na()
tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
d_all <- d_all %>% 
  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4 ), by="datetime")
```
## Range per months

@@

```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize ph_calc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at)%>%
  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb_mix))
pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")

@@

```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
# Compare Lueker and Sulpis using mean discrete values
# first, order columns
d_all <- d_all %>% 
  dplyr::select(order(colnames(d_all))) %>% 
  dplyr::select(datetime, date, year, monthd, montht, everything())
# calculate means of discrete values
mean_ct <- mean(discrete$ct, na.rm = TRUE)
mean_at <- mean(discrete$at, na.rm = TRUE)
mean_pco2 <- mean(discrete$pco2_calc_fb, na.rm = TRUE)
mean_sal <- mean(discrete$sal_fb_mix, na.rm = TRUE)
mean_temp <- mean(discrete$temp_fb, na.rm = TRUE)
mean_discrete <- tibble(mean_ct = mean_ct, mean_at = mean_at, mean_pco2 = mean_pco2, mean_sal = mean_sal, mean_temp = mean_temp)

@@

  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
  dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb_mix, temp_fb) %>% 

@@

                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",

@@

                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",

@@

                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",

@@

                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",

@@

  #               ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb_mix, temp_fb) %>%

@@

carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 

@@

carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 

@@

carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 

@@

  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb_mix, temp_fb) %>% 
